Applying LIME to Bullet Data Research Journal

### 2019-01-17 journal/applying LIME to bullet data journal.Rmd
finished updating journal and edited all possible code to work with tree results

```{r}
# Load libraries
library(tidyverse)
library(bulletr)
library(randomForest)
library(lime)
library(caret)
library(cowplot)
library(purrr)
library(future)
library(furrr)

@@

@@

# Create an explainer object
caret_explainer <- lime(iris_train, caret_model)

# Explain new observation
caret_explanation <- explain(iris_test, caret_explainer, n_labels = 1, n_features = 4)

@@

# Create an explainer object
rf_explainer <- lime(iris_train, model = as_classifier(rf_model))

# Explain new observation
rf_explanation <- explain(iris_test, rf_explainer, n_labels = 1, n_features = 4)
```

@@

@@

## Functions

Heike wrote the function `treebink` to take x and y variables for fitting a tree and returning the cuts for $k$ bins based on the splits from the tree. Here is an example using the function below with the predictor variable of ccf.

@@

I wrote the function `mylime`, which adds an option in the `lime` function from the LIME package to use Heike's function `treebink` to obtain tree based bins. The output from `mylime` can then be input into the `explain` function to obtain explanations. I was able to rerun all of the code for creating the `hamby224_test_explain` dataset with the explanations from the tree based bins included for 2 to 6 bins. I've been working on redoing code from earlier in this journal to work for the added binning method.

There seems to be a problem with `treebink` with certain variables with high enough bins. The function returns more than the desired number of bins. Heike is going to look into this.

@@

When we began looking at the explanations from `lime` with the default settings, we did not think that they made sense. This led me to try applying LIME with a handful of input values. However, since LIME is based on random permutations, I was curious to know how consistent the results were. This led me to try running each implementation for specific starting values a handful of times. The next two sections consider the results from these studies.

@@

The figures in this section are created from the implementations of LIME on the set 1 from the training data for the input options of 2 to 6 quantile bins, 2 to 6 equally spaced bins, kernel density estimation, and normal distribution approximation. Each set of input values was only run once.

@@

The plot below compares the predictions from the "simple model" (the ridge regression model) and the "complex model" (the random forest `rtrees`) on the x-axis from the lime implementations with bin estimation (`bin_continuous == TRUE`). The simple model predictions are on the y-axis, and the complex model predictions are on the x-axis. The plot is faceted by number of bins and whether or not the bins are equally spaced or based on quantiles. The points are colored by the $R^2$ value from the fit of the simple model. The lines are linear regression lines fit to the data points within a facet. We would hope that there is a linear relationship between these two variables. None of the cases show strong linear trends, but some are more linear than others. The quantile bins show that the simple model never makes a prediction over 0.6, whereas the random forest model can have predictions of up to 1. The equally spaced bins do have probabilities that exceed 0.6, but only with 3 and 6 bins. I noticed that within the facets, the points are in mostly horizontal strips, and the number of strips is about the number of bins from the lime implementation.

@@

The plot below shows the absolute value of the difference between the complex model prediction and the simple model prediction versus the complex model prediction. The points are faceted by number of bins and whether the bins are equally spaced or based on quantiles. Again, the points are colored by the $R^2$ values from the simple model. All cases show a v-shaped trend. The low part of the v occurs around a random forest score of about 0.25. That is, the simple model is most accurately portraying the complex model predictions around the random forest score of 0.25. It gets worse near the extremes. However, it is interesting to note that with the equally spaced bins, the absolute difference decreases near 1 for 3 to 6 bins. This is not the case with the quantile bins. It appears that the equally spaced bins are able to make slightly better predictions than the quantile bins when there is a high probability of a match.

@@

## Variability

In order to assess how variable the LIME results are, I ran each of the 12 input situations 10 times. I wanted to look at the variability of the mse for each situation, and I wanted to see how consistent the choice of selected features is by LIME.

@@

  # Specify the number of reps and input cases
  nreps = 10
  noptions = 12

  # Specify the inputs for the sensitivity analysis
  hamby224_sensitivity_inputs <- data.frame(bin_continuous = c(rep(TRUE, nreps * 10), 
                                                      rep(FALSE, nreps * 2)),
                                   quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
                                                     rep(TRUE, nreps * 2)),
                                   nbins = c(rep(rep(2:6, each = nreps), 2), 
                                             rep(4, nreps * 2)),
                                   use_density = c(rep(TRUE, nreps * 11), 
                                                   rep(FALSE, nreps))) %>%
    mutate(case = 1:(nreps * noptions)) %>%
    select(case, bin_continuous, nbins, quantile_bins, use_density)

  # Tell R to run the upcoming code in parallel
  plan(multiprocess)

  # Run lime for the sensitivity analysis
  hamby224_sensitivity_outputs <- future_pmap(.l = as.list(hamby224_sensitivity_inputs %>%
                                                             select(-case)),
             .f = run_lime, # run_lime is one of my helper functions
             train = hamby173and252_train %>% select(rf_features),
             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
             rfmodel = as_classifier(rtrees),
             label = "TRUE",
             nfeatures = 3,
             seed = FALSE) %>%
    map_df(function(list) list$explain) %>%
    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
                            noptions))) %>%
    full_join(hamby224_test %>% na.omit() %>% 
                mutate(case = as.character(case)), by = "case") %>%
    mutate(case = factor(case)) %>%
    select(case, model_r2:feature_weight, bin_continuous:rep, set:land2, rfscore, samesource)

@@

```{r}
joined_results <- hamby224_lime_results %>%
  ungroup() %>%
  mutate(nbins = as.numeric(as.character(nbins))) %>%
  mutate(situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE, 
                            sprintf("%.0f quantile bins", nbins),
                            ifelse(bin_continuous == TRUE & quantile_bins == FALSE, 
                                   sprintf("%.0f equally spaced bins", nbins),
                                   ifelse(bin_continuous == FALSE & use_density == TRUE, 
                                          "kernel density", "normal approximation")))) %>%
  mutate(situation = fct_relevel(situation, 
                                 "2 quantile bins", 
                                 "3 quantile bins",
                                 "4 quantile bins",
                                 "5 quantile bins",
                                 "6 quantile bins")) %>%
  select(set, situation, mse, ave_r2) %>%
  full_join(hamby224_sensitivity_mses %>%
              group_by(set, situation) %>%
              summarise(mean_sensitivity_mse = mean(mse), 
                        sd_sensitivity_mse = sd(mse)),
            by = c("set", "situation")) %>%
  full_join(hamby224_consistency %>% select(set, situation, mean_nlevels, sd_nlevels), 
            by = c("set", "situation")) %>%
  group_by(set) %>%
  mutate(mse_order = dense_rank(mse),
         ave_r2_order = dense_rank(desc(ave_r2)),
         mean_sensitivity_mse_order = dense_rank(mean_sensitivity_mse),
         mean_nlevels_order = dense_rank(mean_nlevels))
```

@@

## Heike's Suggestions

* We talked about including the penalty for the number of parameters in the discussion of the paper.
* We talked about using a tree to choose the bins. This would allow us to automate the process and to obtain a penalty parameter since the trees give us nesting. (MSE + lambda * p where p is the from the number of trees multiplied by the number of ...)
* Look at the AUC after binning

## Results from One Implementation

```{r}
# Selects only the top features for the cases where binning was used
top_features <- hamby224_test_explain %>%
  filter(bin_situation != "other") %>%
  select(set, situation, bin_situation, case, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, desc(feature_weight_abs)) %>%
  group_by(situation, case) %>%
  slice(1)

# Plots the top feature for each case for each bin situation
ggplot(top_features, aes(x = situation, y = case, fill = feature)) + 
  geom_tile() + 
  facet_grid(set ~ bin_situation, scales = "free") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_brewer(palette = "Blues")

# Plots the proportions of number of top features chosen across number of bins for a case
# within a binning method
top_features %>%
  group_by(set, case, bin_situation) %>%
  summarise(nfeatures = length(levels(factor(feature)))) %>%
  ggplot(aes(x = bin_situation, fill = factor(nfeatures))) + 
  geom_bar(position = "stack") + 
  facet_grid(set ~ .) + 
  theme_bw() +
  scale_fill_brewer(palette = "Blues")
```

## Assessing Variability

In order to assess how variable the LIME results are, I ran each of the 12 input situations 10 times. I wanted to look at the variability of the mse for each situation, and I wanted to see how consistent the choice of selected features is by LIME.

  # Specify the number of reps and input cases
  nreps = 10
  noptions = 12

  # Specify the inputs for the sensitivity analysis
  hamby224_sensitivity_inputs <- data.frame(bin_continuous = c(rep(TRUE, nreps * 10), 
                                                      rep(FALSE, nreps * 2)),
                                   quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
                                                     rep(TRUE, nreps * 2)),
                                   nbins = c(rep(rep(2:6, each = nreps), 2), 
                                             rep(4, nreps * 2)),
                                   use_density = c(rep(TRUE, nreps * 11), 
                                                   rep(FALSE, nreps))) %>%
    mutate(case = 1:(nreps * noptions)) %>%
    select(case, bin_continuous, nbins, quantile_bins, use_density)

  # Tell R to run the upcoming code in parallel
  plan(multiprocess)

  # Run lime for the sensitivity analysis
  hamby224_sensitivity_outputs <- future_pmap(.l = as.list(hamby224_sensitivity_inputs %>%
                                                             select(-case)),
             .f = run_lime, # run_lime is one of my helper functions
             train = hamby173and252_train %>% select(rf_features),
             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
             rfmodel = as_classifier(rtrees),
             label = "TRUE",
             nfeatures = 3,
             seed = FALSE) %>%
    map_df(function(list) list$explain) %>%
    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
                            noptions))) %>%
    full_join(hamby224_test %>% na.omit() %>% 
                mutate(case = as.character(case)), by = "case") %>%
    mutate(case = factor(case)) %>%
    select(case, model_r2:feature_weight, bin_continuous:rep, set:land2, rfscore, samesource)

>>>>

```{r}
# Load libraries
library(bulletr)
library(caret)
library(cowplot)
library(furrr)
library(future)
library(lime)
library(plotly)
library(purrr)
library(randomForest)
library(tidyverse)

@@

I also wrote some code to create the above plot using individual plots instead of facets. This is included below (but not executed).

```{r eval = FALSE}
# Code for creating the heatmap plots using individual plots

# Input data
hamby224_test_explain <- readRDS("./data/hamby224_test_explain.rds")

# Create a dataset with all combinations of lands and bullets comparisons for each set
combinations1 <- data.frame(set = factor(1),
                            expand.grid(land1 = factor(1:6),
                                        land2 = factor(1:6),
                                        bullet1 = factor(c("1", "2", "Q")),
                                        bullet2 = factor(c("1", "2", "Q"))))
combinations11 <- data.frame(set = factor(11),
                             expand.grid(land1 = factor(1:6),
                                         land2 = factor(1:6), 
                                         bullet1 = factor(c("1", "2", "I")),
                                         bullet2 = factor(c("1", "2", "I"))))
combinations <- rbind(combinations1, combinations11)

# Join the combinations and the data so that all combinations have a row in the data
hamby224_test_explain_NAs <- left_join(combinations, hamby224_test_explain,
                                       by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
  mutate(bullet1 = forcats::fct_recode(bullet1, "Known 1" = "1", "Known 2" = "2", 
                                       "Questioned" = "Q", "Questioned" = "I"),
         bullet2 = forcats::fct_recode(bullet2, "Known 1" = "1", "Known 2" = "2", 
                                       "Questioned" = "Q", "Questioned" = "I"))

chosen_set = 1

p1 <- hamby224_test_explain_NAs %>%
  filter(set == chosen_set, bullet1 == "Known 1", bullet2 == "Known 1") %>%
  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
  distinct() %>%
  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
  geom_tile(aes(fill = rfscore)) +
  facet_grid(bullet1 ~ bullet2, scales = "free") +
  theme_minimal() +
  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
  theme(legend.position = "none")

p2 <- hamby224_test_explain_NAs %>%
  filter(set == chosen_set, bullet1 == "Known 1", bullet2 == "Known 2") %>%
  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
  distinct() %>%
  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
  geom_tile(aes(fill = rfscore)) +
  facet_grid(bullet1 ~ bullet2, scales = "free") +
  theme_minimal() +
  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
  theme(legend.position = "none")

p3 <- hamby224_test_explain_NAs %>%
  filter(set == chosen_set, bullet1 == "Known 1", bullet2 == "Questioned") %>%
  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
  distinct() %>%
  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
  geom_tile(aes(fill = rfscore)) +
  facet_grid(bullet1 ~ bullet2, scales = "free") +
  theme_minimal() +
  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
  theme(legend.position = "none")

p4 <- ggplot() + geom_blank() + theme_classic()

p5 <- hamby224_test_explain_NAs %>%
  filter(set == chosen_set, bullet1 == "Known 2", bullet2 == "Known 2") %>%
  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
  distinct() %>%
  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
  geom_tile(aes(fill = rfscore)) +
  facet_grid(bullet1 ~ bullet2, scales = "free") +
  theme_minimal() +
  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
  theme(legend.position = "none")

p6 <- hamby224_test_explain_NAs %>%
  filter(set == chosen_set, bullet1 == "Known 2", bullet2 == "Questioned") %>%
  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
  distinct() %>%
  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
  geom_tile(aes(fill = rfscore)) +
  facet_grid(bullet1 ~ bullet2, scales = "free") +
  theme_minimal() +
  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
  theme(legend.position = "none")

p7 <- ggplot() + geom_blank() + theme_classic()

p8 <- ggplot() + geom_blank() + theme_classic()

p9 <- hamby224_test_explain_NAs %>%
  filter(set == chosen_set, bullet1 == "Questioned", bullet2 == "Questioned") %>%
  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
  distinct() %>%
  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
  geom_tile(aes(fill = rfscore)) +
  #facet_grid(bullet1 ~ bullet2, scales = "free") +
  theme_minimal() +
  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5, limits = c(0,1)) +
  labs(x = "Land 1", y = "Land 2", fill = "RF Score")

style(subplot(p1, p2, p3, p4, p5, p6, p7, p8, p9, nrows = 3, titleX = TRUE, titleY = TRUE, margin = 0.03),
      hoverinfo = "skip",
      traces = 7)
```

@@

# Create an explainer object
caret_explainer <- lime::lime(iris_train, caret_model)

# Explain new observation
caret_explanation <- lime::explain(iris_test, caret_explainer, n_labels = 1, n_features = 4)

@@

# Create an explainer object
rf_explainer <- lime::lime(iris_train, model = as_classifier(rf_model))

# Explain new observation
rf_explanation <- lime::explain(iris_test, rf_explainer, n_labels = 1, n_features = 4)
```

@@

# Subsampled Bins

One idea that I had to try to improve the lime explanations was to subsample from the training dataset before computing the quantiles. The proportion of observations with `samesource = FALSE` is very large in the training dataset, so that overwhelms the observations with `samesource = TRUE`. By subsampling, it might allow for better locations to bin the data. I wrote the code below to attempt to apply lime to a subsampled version of the training dataset.

```{r eval = FALSE}
# Code saved for future use for the sampling data

# Create the data (with a set seed)
set.seed(20181128)
hamby173and252_train_sub <- hamby173and252_train %>%
  filter(samesource == FALSE) %>%
  slice(sample(1:length(hamby173and252_train$barrel1), 4500, replace = FALSE)) %>%
  bind_rows(hamby173and252_train %>% filter(samesource == TRUE))

# Save the subsampled data
write.csv(hamby173and252_train_sub, "../data/hamby173and252_train_sub.csv", row.names = FALSE)

# Apply lime to the subsampled training data with the specified input options
hamby224_lime_explain_sub <- future_pmap(.l = as.list(hamby224_lime_inputs %>%
                                                        select(-case)),
                                         .f = run_lime, # run_lime is one of my helper functions
                                         train = hamby173and252_train_sub %>% select(rf_features),
                                         test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
                                         rfmodel = as_classifier(rtrees),
                                         label = "TRUE",
                                         nfeatures = 3,
                                         seed = TRUE) %>%
  mutate(training_data = factor("Subsampled"))

# Separate the lime and explain function results from the subsampled data
hamby224_lime_sub <- map(hamby224_lime_explain_sub, function(list) list$lime)
hamby224_explain_sub <- map_df(hamby224_lime_explain_sub, function(list) list$explain)

# Join the lime results from the full and subsampled training data
hamby224_lime <- c(hamby224_lime_full, hamby224_lime_sub)
hamby224_explain <- bind_rows(hamby224_explain_full, hamby224_explain_sub)
```

@@

Heike suggested the idea of using classification trees to choose the cutoffs for the lime bins. That is, the divisions in the tree could be used as the bin cuts. This would allow us to automate the process and to obtain a penalty parameter since the trees give us nesting. (MSE + lambda * p where p is the from the number of trees multiplied by the number of ...)

Heike wrote the function `treebink` to take x and y variables for fitting a tree and returning the cuts for $k$ bins based on the splits from the tree. The function is stored in the file   `helper_functions.R`. Here is an example using the function below with the predictor variable of ccf.

@@

However, there seems to be a problem with `treebink`. For certain variables, when a high number of bins is requessted, the function returns more than the desired number of bins. Heike is going to look into this.

I wrote the function `mylime`, which adds an option in the `lime` function from the LIME package to use Heike's function `treebink` to obtain tree based bins. This function is also included in the file `helper_functions.R`. The output from `mylime` can then be input into the `explain` function to obtain explanations. I was able to rerun all of the code for creating the `hamby224_test_explain` dataset with the explanations from the tree based bins included for 2 to 6 bins.

@@

When we began looking at the explanations from `lime` with the default settings, we did not think that they made sense. This led me to try applying LIME with a handful of input values. I also have tried running LIME with the tree based bins. Additionally, since LIME is based on random permutations, I was curious to know how consistent the results were. This led me to try running each implementation a handful of times. I have attempted to evaulate these results by both considering the accuracy and consistency of the results.

@@

The figures in this section are created from the implementations of LIME on set 1 from the training data for the input options of 2 to 6 quantile bins, 2 to 6 equally spaced bins, 2 to 6 tree based bins, kernel density estimation, and normal distribution approximation. Each set of input values was only run once.

@@

The plot below compares the predictions from the "simple model" (the ridge regression model) and the "complex model" (the random forest `rtrees`) on the x-axis from the lime implementations with bin estimation (`bin_continuous == TRUE`). The simple model predictions are on the y-axis, and the complex model predictions are on the x-axis. The plot is faceted by number of bins and the type of bin. The points are colored by the $R^2$ value from the fit of the simple model. The lines are linear regression lines fit to the data points within a facet. We would hope that there is a linear relationship between these two variables. None of the cases show strong linear trends, but some are more linear than others. The quantile bins show that the simple model never makes a prediction over 0.6, whereas the random forest model can have predictions of up to 1. The equally spaced bins do have probabilities that exceed 0.6, but only with 3 and 6 bins. The tree based bins do the best job with predictions above 0.6 for all number of bins. The tree bins also seem to group the simple model predictions into two categories (probably based on the samesource variable). I noticed that within the facets, the points are in mostly horizontal strips, and the number of strips is about the same as the number of bins from the lime implementation.

@@

The plot below shows the absolute value of the difference between the complex model prediction and the simple model prediction versus the complex model prediction. The points are faceted by number of bins and bin type. Again, the points are colored by the $R^2$ values from the simple model. All cases show a v-shaped trend. The low part of the v occurs around a random forest score of about 0.25. That is, the simple model is most accurately portraying the complex model predictions around the random forest score of 0.25. It gets worse near the extremes. However, it is interesting to note that with the equally spaced bins and the tree based bins, the absolute difference decreases near 1. This is not the case with the quantile bins. It appears that the equally spaced bins and tree based bins are able to make slightly better predictions than the quantile bins when there is a high probability of a match.

@@

## Consistency with One Implementation

```{r}
# Selects only the top features for the cases where binning was used
top_features <- hamby224_test_explain %>%
  filter(bin_situation != "other") %>%
  select(set, situation, bin_situation, nbins, case, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, desc(feature_weight_abs)) %>%
  group_by(situation, case) %>%
  slice(1)
```

```{r}
# Plots the top feature for each case for each bin situation
ggplot(top_features, aes(x = situation, y = case, fill = feature)) + 
  geom_tile() + 
  facet_grid(set ~ bin_situation, scales = "free") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_brewer(palette = "Blues")
```

```{r}
# Plots the proportions of number of top features chosen across number of bins for a case
# within a binning method
top_features %>%
  group_by(set, case, bin_situation) %>%
  summarise(nfeatures = length(levels(factor(feature)))) %>%
  ggplot(aes(x = bin_situation, fill = factor(nfeatures))) + 
  geom_bar(position = "stack") + 
  facet_grid(set ~ .) + 
  theme_bw() +
  scale_fill_brewer(palette = "Blues")
```

## Consistency Across Implementations

In order to assess how variable the LIME results are, I ran each of the 17 input situations 10 times. I wanted to look at the variability of the mse for each situation, and I wanted to see how consistent the choice of selected features is by LIME.

@@

  # Specify the number of reps and input cases
  nreps = 10
  noptions = 17

  # Specify the inputs for the sensitivity analysis
  hamby224_sensitivity_inputs <- list(bin_continuous = c(rep(TRUE, nreps * 15),
                                                         rep(FALSE, nreps * 2)),
                                      quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
                                                        rep(TRUE, nreps * 7)),
                                      nbins = c(rep(rep(2:6, each = nreps), 3), 
                                                rep(4, nreps * 2)),
                                      use_density = c(rep(TRUE, nreps * 16), 
                                                      rep(FALSE, nreps)),
                                      bin_method = c(rep("quantile_bins", nreps * 5),
                                                      rep("equally_spaced", nreps * 5),
                                                      rep("tree", nreps * 5),
                                                      rep("quantile_bins", nreps * 2)))
  # Tell R to run the upcoming code in parallel
  plan(multiprocess)

  # Run lime for the sensitivity analysis
  hamby224_sensitivity_outputs <- future_pmap(.l = hamby224_sensitivity_inputs,
             .f = run_lime, # run_lime is one of my helper functions
             train = hamby173and252_train %>% select(rf_features),
             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
             response = hamby173and252_train$samesource,
             rfmodel = as_classifier(rtrees),
             label = "TRUE",
             nfeatures = 3,
             seed = FALSE) %>%
    map_df(function(list) list$explain) %>%
    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
                            noptions))) %>%
    full_join(hamby224_test %>% na.omit() %>% 
                mutate(case = as.character(case)), by = "case") %>%
    mutate(case = factor(case)) %>%
    select(case, model_r2:feature_weight, bin_continuous:rep, set:land2, rfscore, samesource)

  hamby224_sensitivity_inputs <- hamby224_sensitivity_inputs %>%
    unlist() %>%
    matrix(ncol = length(hamby224_sensitivity_inputs), 
           dimnames = list(NULL, names(hamby224_sensitivity_inputs))) %>%
    as.data.frame() %>%
    mutate(case = 1:(nreps * noptions)) %>%
    select(case, bin_continuous:bin_method)

@@

```{r}
joined_results <- hamby224_lime_results %>%
  select(set, situation, mse, ave_r2) %>%
  full_join(hamby224_sensitivity_mses %>%
              group_by(set, situation) %>%
              summarise(mean_sensitivity_mse = mean(mse), 
                        sd_sensitivity_mse = sd(mse)),
            by = c("set", "situation")) %>%
  full_join(hamby224_consistency %>% select(set, situation, mean_nlevels, sd_nlevels), 
            by = c("set", "situation")) %>%
  group_by(set) %>%
  mutate(mse_order = dense_rank(mse),
         ave_r2_order = dense_rank(desc(ave_r2)),
         mean_sensitivity_mse_order = dense_rank(mean_sensitivity_mse),
         mean_nlevels_order = dense_rank(mean_nlevels))
```

@@

# Heike's Suggestions

* We talked about including the penalty for the number of parameters in the discussion of the paper.
* Look at the AUC after binning
